Analysis paper

### 2021-04-08 analysis/analysis.Rmd
update analysis with some todos

truth_vs_forecast_2 <- df %>%
  ggplot(aes(y = true_value, x = target_end_date)) + 
  geom_linerange(aes(ymin = `0.025`, ymax = `0.975`, color = model), 
                 size = 1.5,
                 alpha = 0.4,
                 position = position_dodge(width = 3)) + 
  geom_linerange(aes(ymin = `0.25`, ymax = `0.75`, color = model), 
                 size = 1.5,
                 alpha = 0.8,
                 position = position_dodge(width = 3)) + 
  labs(y = "value", x = "date") + 
  geom_point() + 
  geom_line() + 
  theme_light() + 
  facet_grid(target_type ~ location_name, scales = "free") + 
  theme(legend.position = "bottom")

@@

```{r}
### same plot with mean score ratio
rel_skill_time_2 <- scores_target_forecastdate  %>%
  ggplot(aes(x = as.Date(forecast_date), y = scaled_rel_skill, colour = model)) + 
  geom_line() + 
  geom_point() + 
  theme_light() + 
  facet_grid(target_type ~ location_name, scales = "free") +
  theme(legend.position = "bottom") +
  labs(y = "relative skill", x = "date")

@@

```{r fig.height=10, fig.width=20}
# glue two plots together
truth_vs_forecast_2 + rel_skill_time_2
ggsave(here("analysis", "plots", "figure-forecasts-2.png"))
```

@@

- [ ] make plot nicer

@@

@@

>>>>

truth_vs_forecast_2 <- df %>%
  ggplot(aes(y = true_value, x = target_end_date, colour = model, fill = model)) + 
  geom_linerange(aes(ymin = `0.025`, ymax = `0.975`, color = model), 
                 size = 1.5,
                 alpha = 0.4,
                 position = position_dodge(width = 3)) + 
  geom_linerange(aes(ymin = `0.25`, ymax = `0.75`, color = model), 
                 size = 1.5,
                 alpha = 0.8,
                 position = position_dodge(width = 3)) + 
  labs(y = "value", x = "date") + 
  geom_point() + 
  geom_line() + 
  theme_light() + 
  facet_grid(target_type ~ location_name, scales = "free") + 
  theme(legend.position = "bottom")

@@

```{r}
### same plot with mean score ratio
rel_skill_time_2 <- scores_target_forecastdate  %>%
  ggplot(aes(x = as.Date(forecast_date), y = scaled_rel_skill, fill = model, colour = model)) + 
  geom_line() + 
  geom_point() + 
  theme_light() + 
  facet_grid(target_type ~ location_name, scales = "free") +
  theme(legend.position = "bottom") +
  labs(y = "relative skill", x = "date")

@@

```{r fig.height=16, fig.width=8}
# glue two plots together
truth_vs_forecast_2 / rel_skill_time_2 + 
  plot_layout(guides = "collect") & theme(legend.position = 'bottom') 
ggsave(here("analysis", "plots", "figure-forecasts-2.png"))
```

@@

- [ ] make plot nicer
- [ ] maybe make this with relative skill instead
- [ ] finish this todo list
- [ ] maybe a density plot instead of a ridge plot?

@@

- [ ] have the second plot stratified by epidemic period

@@

- maybe make tihs a PIT plot
- stratify by period
